What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Enclos class added for synthetic environments
Enclosure
Update provenance numbers

% Add a table with the distribution of types of expr_resolved?

@@

Synthetic environments need a parent. It is specified as an argument of the \c{new.env} function, or when \c{envir} is a list or a data frame, \eval uses its third argument
(\c{enclos}) as the parent.  The parent is used to lookup variables not found in its
child (side effects go to the child only). Table~\ref{tab:newenvs} shows the
kinds of the parents of synthetic environments. Over half are functions, then
come packages and global.

@@

\begin{compactitem}[---]
\item {\it Reflection:} This group corresponds to uses of the \c{match.call}
  function to reflectively capture the expression that invoked the current
  function.
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression}. Function arguments are passed as
  promises and \c{substitute} is used to retrieve the source expression
  associated with the promise.
\item {\it String:} Finally, expressions can be created from strings by invoking
   \c{parse}, \c{str2expression} or \c{str2lang}.
\end{compactitem}

@@

\begin{wraptable}{r}{5cm}\small\centering
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Constructed & \packageNbConstructedSites & \packageNbConstructedSitePercent \\
String & \packageNbStringSites & \packageNbStringSitePercent \\
Reflection &  \packageNbMatchCallExprsSites & \packageMatchCallExprsSitePercent\\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{wraptable}

>>>>

@@

Synthetic environments need a parent. It is specified as an argument of the \c{new.env} function, or when \c{envir} is a list or a data frame, \eval uses its third argument
(\c{enclos}) as the parent.  The parent is used to lookup variables not found in its
child (side effects go to the child only). Table~\ref{tab:newenvs} shows the
kinds of the parents of synthetic environments. Most of them are functions, then
come global and package.

@@

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression}. Function arguments are passed as
  promises and \c{substitute} is used to retrieve the source expression
  associated with the promise.
  \item {\it Reflection:} This group corresponds to uses of the \c{match.call}
  function to reflectively capture the expression that invoked the current
  function.
\item {\it String:} Finally, expressions can be created from strings by invoking
   \c{parse}, \c{str2expression} or \c{str2lang}.
\end{compactitem}

@@

\begin{wraptable}{r}{5cm}\small\centering
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Constructed & \packageNbConstructedSites & \packageNbConstructedSitePercent \\
Reflection &  \packageNbMatchCallExprsSites & \packageMatchCallExprsSitePercent\\
String & \packageNbStringSites & \packageNbStringSitePercent \\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{wraptable}
